Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2021-03-04 paper/main.tex
Update undefined calls
Use asmsmall document class (OOPSLA)

\documentclass[USenglish,cleveref, autoref, thm-restate]{lipics-v2019}
\usepackage{listings,hyperref,multirow,paralist,xspace,url,wrapfig}
\input{macro}
\newcommand{\mypara}[1]{\medskip\noindent\emph{#1}\xspace}
\newcommand{\NOTE}[1]{{\it Note: #1}\xspace}

\title{Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R}
\titlerunning{Why Eval (in R)?}

\begin{document}
\maketitle

@@

@@

\mypara{Limitations.}
%
% We turn off the bytecode compiler for this study. The bytecode
% compiler can also call \eval.
%
We do not get source locations for \UndefinedEvalsRnd UPDATE!! \eval calls. In
these cases \eval is either passed as an argument to a higher-order functions or
is defined in a function returned by a higher-order function, or it can be a
generated called from package native code. However, this is a meager
\PercentUndefinedEval UPDATE!! of all \eval calls and is unlikely to affect our
analysis. We ignore calls to the native \eval function exposed by R. We also
ignore the \c{rlang::tidy_eval} function which uses native \eval internally
because \c{rlang} is used to implement a DSL for data analysis in R. It
introduces a new first-class promise object called \c{quosure} for which it
implements special evaluation support in \c{tidy_eval}.

>>>>

%\documentclass[USenglish,cleveref, autoref, thm-restate]{lipics-v2019}
\documentclass[acmsmall]{acmart}
\usepackage{listings,hyperref,multirow,paralist,xspace,url,wrapfig}
\input{macro}
\newcommand{\mypara}[1]{\medskip\noindent\emph{#1}\xspace}
\newcommand{\NOTE}[1]{{\it Note: #1}\xspace}

\begin{document}

\title{Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R}
%\titlerunning{Why Eval (in R)?}

\author{Author }
\authornote{Both authors contributed equally to this research.}
\email{a@b.com}
\orcid{}
\author{Author}
\authornotemark[1]
\email{r@s.com}
\affiliation{%
	\institution{Institute for Clarity in Documentation}
	\streetaddress{P.O. Box 1212}
	\city{Dublin}
	\state{Ohio}
	\country{USA}
	\postcode{43017-6221}
}

@@

\maketitle

@@

\mypara{Limitations.}
%
% We turn off the bytecode compiler for this study. The bytecode
% compiler can also call \eval.
%
We do not get source locations for \CranUndefinedRnd \eval calls. In
these cases \eval is either passed as an argument to a higher-order functions or
is defined in a function returned by a higher-order function, or it can be a
generated called from package native code. However, this is a meager
\CranUndefinedRatio of all \eval calls and is unlikely to affect our
analysis. We ignore calls to the native \eval function exposed by R. We also
ignore the \c{rlang::tidy_eval} function which uses native \eval internally
because \c{rlang} is used to implement a DSL for data analysis in R. It
introduces a new first-class promise object called \c{quosure} for which it
implements special evaluation support in \c{tidy_eval}.
